Cryptographic assurance of secrecy and fairness in voting

### 2012-12-06 paper/paper.tex
Use feminine singular pronouns.
I previously missed instances of "he/she".

When casting a ballot, a voter knows which candidate(s) he/she \emph{intended} to vote for -- but
once the ballot is cast, a system that supports verification of vote reporting allows the voter to
compare the recorded vote to what he/she intended to indicate on the ballot.

For example, at an in-person polling location -- ignoring ballot secrecy (see below) -- a voter
could be shown a screen giving the name of the candidate(s) he/she just voted for. If the display
does not match the voter's intention, then the voter can ``try again'' -- or call into question the
entire vote collection process.

@@

After a ballot has been cast, and the voter has left the polling place, how can he/she be certain
that the ballot used in the final count is what he/she actually cast? (This could be a problem even
if the user has verified the \emph{recording} of the vote.)

It is possible -- as we shall see -- for a voting system to allow a voter to check that the ballot
he/she cast is exactly what was considered during vote counting.

@@

When a voter goes to cast a vote, her candidate selection is encrypted locally (i.e., on her
computer terminal, in the browser) using ElGamal. Prior to casting the ballot, the voter is
presented with a SHA-1 hash of her encrypted ballot. At this point, the voter may choose either
to submit the ballot or to ``audit'' it. In the former case, the ballot is cast and voting is
complete. But when a voter chooses to ``audit,'' he/she is presented with \emph{all} of the data
used to encrypt the vote. Namely, this includes the public key and the ``randomness'' that were used
by an implementation of ElGamal to encrypt the vote. The voter can then -- using a modified ElGamal
which allows randomness to be specified -- perform the encryption and SHA-1 hash herself
to verify that the hash that \emph{would} have been cast actually does represent the ballot he/she
intended to cast.

@@

Helios does not actually permit a voter to verify the ballot that he/she actually casts. Rather, it
allows users to verify a ballot without casting it (after which point it cannot be cast without
a new encryption). The assumption here is that \emph{some} voter will choose to audit a ballot, and
so the system cannot simply cheat and show the user a predetermined hash: it \emph{must} be a valid
one -- otherwise the deception would be revealed should the voter choose to exercise her right
to audit.

@@

Scantegrity prevents coercion via the manner it uses to ``encrypt'' ballots. Once cast, a ballot's
ciphertext is \emph{always public}. A voter can claim that he/she voted in a particular manner, but
without exposure of the data maintained in Table P -- Scantegrity's ``secret'' -- the voter has no
way to prove to a third party that the claim is true.

@@

Compared to traditional voting systems, each of the schemes we have examined provides voters a
greater assurance that their votes \emph{are} counted and that the election authority has
\emph{properly} counted all votes that were cast. By satisfying the various facets of ballot
secrecy, they also serve to enforce practices that in general must only be assumed: that voters
cannot be coerced and that a voter is never required to reveal the candidate for whom he/she voted.

>>>>

When casting a ballot, a voter knows which candidate(s) she \emph{intended} to vote for -- but
once the ballot is cast, a system that supports verification of vote reporting allows the voter to
compare the recorded vote to what she intended to indicate on the ballot.

For example, at an in-person polling location -- ignoring ballot secrecy (see below) -- a voter
could be shown a screen giving the name of the candidate(s) she just voted for. If the display
does not match the voter's intention, then the voter can ``try again'' -- or call into question the
entire vote collection process.

@@

After a ballot has been cast, and the voter has left the polling place, how can she be certain
that the ballot used in the final count is what she actually cast? (This could be a problem even
if the user has verified the \emph{recording} of the vote.)

It is possible -- as we shall see -- for a voting system to allow a voter to check that the ballot
she cast is exactly what was considered during vote counting.

@@

When a voter goes to cast a vote, her candidate selection is encrypted locally (i.e., on her
computer terminal, in the browser) using ElGamal. Prior to casting the ballot, the voter is
presented with a SHA-1 hash of her encrypted ballot. At this point, the voter may choose either
to submit the ballot or to ``audit'' it. In the former case, the ballot is cast and voting is
complete. But when a voter chooses to ``audit,'' she is presented with \emph{all} of the data
used to encrypt the vote. Namely, this includes the public key and the ``randomness'' that were used
by an implementation of ElGamal to encrypt the vote. The voter can then -- using a modified ElGamal
which allows randomness to be specified -- perform the encryption and SHA-1 hash herself
to verify that the hash that \emph{would} have been cast actually does represent the ballot she
intended to cast.

@@

Helios does not actually permit a voter to verify the ballot that she actually casts. Rather, it
allows users to verify a ballot without casting it (after which point it cannot be cast without
a new encryption). The assumption here is that \emph{some} voter will choose to audit a ballot, and
so the system cannot simply cheat and show the user a predetermined hash: it \emph{must} be a valid
one -- otherwise the deception would be revealed should the voter choose to exercise her right
to audit.

@@

Scantegrity prevents coercion via the manner it uses to ``encrypt'' ballots. Once cast, a ballot's
ciphertext is \emph{always public}. A voter can claim that she voted in a particular manner, but
without exposure of the data maintained in Table P -- Scantegrity's ``secret'' -- the voter has no
way to prove to a third party that the claim is true.

@@

Compared to traditional voting systems, each of the schemes we have examined provides voters a
greater assurance that their votes \emph{are} counted and that the election authority has
\emph{properly} counted all votes that were cast. By satisfying the various facets of ballot
secrecy, they also serve to enforce practices that in general must only be assumed: that voters
cannot be coerced and that a voter is never required to reveal the candidate for whom she voted.
